---
output:
  pdf_document: default
  html_document: default
---
title: "Machine Learning: Predicting Diabetes using Pima Indians Data Set"
author: "Melissa"
date: "June 6, 2020"
output: html_document
---

1. Load the libraries.

```{r}
library(neuralnet)
library(caret)
library(tidyverse)
library(mlbench)
library(e1071)
library(ranger)
tinytex::install_tinytex()
```

2. Store the data frame in an object, go over the structure and do some quick exploratory analysis to see the balance of the data set.

```{r}
data("PimaIndiansDiabetes")
df <- PimaIndiansDiabetes
str(PimaIndiansDiabetes)
ggplot(df, aes(diabetes, fill = as.factor(diabetes))) + geom_bar()
```

3. Create a binary variable for the independent/response variable.  

```{r}
df$binary <- ifelse(df$diabetes == "neg", 0, 1)
```

4. Create a train/test split using caret's createDataPartition function.

```{r}
rows <- createDataPartition(df$binary, times =1,
                            p = .7, list = F)
train <- df[rows,]
test <- df[-rows,]


```

5. Create the model

```{r}

model <- train(as.factor(binary) ~ ., 
               data = train,
               method = "ranger",
               trControl = trainControl(method = "repeatedcv", number = 2, repeats = 2))

model
```

6. Test the model on the Test set and build a confusion matrix.

```{r}
pred_train <- predict(model, train)
pred_test <- predict(model, test)

pred_train

confusionMatrix(pred_train, as.factor(train$binary))
confusionMatrix(pred_test, as.factor(test$binary))
```